---
title: "sc2marker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r fig.align='center',echo=F, warning=FALSE}
suppressMessages(require(DT))
suppressMessages(require(Seurat))
suppressMessages(require(reshape2))
suppressMessages(require(ggplot2))
suppressMessages(require(ggridges))
suppressMessages(require(dplyr))
suppressMessages(library(sc2marker))
source("../src/plot_ridge2.R")
scrna <- readRDS("../../results/sc2marker.all.scrna.intermediate.rds")
markers.all <- readRDS("../../results/sc2marker.all.allmarkers.intermediate.rds")
```


We tried to use [sc2marker](https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-022-04817-5) to find the minimal protein markers to differentiate a certain cell type from the rest of the clusters. 

There are 24 cell types in total in this dataset. Each cell type was provided a list of markers and their corresponding ranking scores. TP: true positives, FP: false positives, TN: true negatives, FN: false negatives. The direction indicates whether the marker is highly (+) / lowly(-) expressed in the specific cell type compared to the rest groups. The x-axis in the ridge plot is in log2(x+1) scale. The red dashed line indicatesd the ranking score for each gene.


# Cluster: `r paste("non-classical monocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "non-classical monocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("classical monocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "classical monocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("CD16-positive, CD56-dim natural killer cell, human")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "CD16-positive, CD56-dim natural killer cell, human"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("natural killer cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "natural killer cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("plasmacytoid dendritic cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "plasmacytoid dendritic cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("conventional dendritic cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "conventional dendritic cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("platelet")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "platelet"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("CD16-negative, CD56-bright natural killer cell, human")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "CD16-negative, CD56-bright natural killer cell, human"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("granulocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "granulocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("intermediate monocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "intermediate monocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("naive B cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "naive B cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("memory B cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "memory B cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("gamma-delta T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "gamma-delta T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("plasmablast")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "plasmablast"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("regulatory T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "regulatory T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("CD4-positive, alpha-beta memory T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "CD4-positive, alpha-beta memory T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("CD8-positive, alpha-beta memory T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "CD8-positive, alpha-beta memory T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("naive thymus-derived CD8-positive, alpha-beta T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "naive thymus-derived CD8-positive, alpha-beta T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("naive thymus-derived CD4-positive, alpha-beta T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "naive thymus-derived CD4-positive, alpha-beta T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("mucosal invariant T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "mucosal invariant T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("memory T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "memory T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("double-positive, alpha-beta thymocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "double-positive, alpha-beta thymocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("double negative thymocyte")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "double negative thymocyte"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

# Cluster: `r paste("T cell")`

## Table

```{r fig.align='center',echo=T, warning=FALSE}
celltype <- "T cell"
markers <- markers.all[[celltype]]; markers$`FP details`=NA
get_antibody(markers, org = "human")
```

## Ridge

```{r fig.align='center',echo=T, warning=FALSE,message=F, fig.width=10, fig.height=8}
plot_ridge2(scrna, id = celltype, genes = markers[1:6,]$gene, 
           aggr.other = FALSE, ncol = 3, assay = "ADT", slot = "data")
```

